\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-09-21 Manuscript/reply.tex
replied to more points, still need to work womens results into discussion

One of the reasons why we did not include data from other sprinting evetns is
because we wanted to ground the article in Devon Allen's story and to be about
the hurdles events.  Athletes who compete in the longer events such as 400 meters
may not have as good of a start as those in the 100 meter events because reaction
time plays a much smaller role in the outcome of the race. While it is common
for amateur and collegiate athletes to compete in multiple sprinting events, it
seems reasonable that a world championship 100 meter runner may be only a top 20
200 meter runner.  We are trying to estimate the probabilty of observing a extreme
reaction time to determine whether 0.1 seconds is fair but if we include data
from competitions with slower reaction times, then 0.1 seconds is going to be
more extreme.

@@

The heat effect measures the speed-level of the heat.  We added some additional
explanations to make it clear what the venue and heat effect refer to. We did
not want to call it a "race effect" as we were worried that may be interpreted
to mean the race of the athlete.

@@

\end{comment}  
We do not have enough evidence to conclude that the sensors were calibrated
differently, so thus we make general recommendations for World Athletics.

@@

We can restructure the paper but doesn't the abstract mention the goals of the
paper? I suppose the introduction is really more of a background section.

@@

Unfortunately data such as this is not easy to come by.  We found as much as we
could online, but there is simply not enough data to justify a formal analysis
of his reaction times across lower level meets.

>>>>

Thank you for these suggestions, we were able to expand the scope of our data
by including results from the men's and women's 100 meter dash.  We considered
adding additional sprinting events such as the 200 meter dash but
when we included a term for type of event in our model the coefficient on this
event term was significant for the 200 meter dash for both men's and women's
data. The coefficient was not signficant when we included the 100 meter dash
results. This is not particularly suprising as athletes who compete in the longer
events may not have as good of a start as those in the 100
meter events because reaction time plays a much smaller role in the outcome of
the race. While it is common for amateur and collegiate athletes to compete in
multiple sprinting events, it seems reasonable that a world championship 100
meter runner may be only a very good 200 meter runner.  We are trying to
estimate the probabilty of observing a extreme reaction time to determine
whether 0.1 seconds is fair but if we include data from competitions with slower
reaction times, then 0.1 seconds is going to be more extreme.  To answer later
thoughts about looking at all sprinting events, we observed boxplots and what we
found were that reaction times in longer sprinting events were much more stable
than in the 100 meter dash and hurdle and thus any insights would likely not be
informative to questioning whether 0.1 seconds is a fair barrier or if athletes
in those events had faster reaction times in 2022.  This follows the conventional
wisdom that athletes are more focuesed on not false starting at the start of the
longer races than they are on getting a perfect start.

@@

The heat effect measures the speed-level of the heat.  We added some additional
explanations to make it clear what the venue and heat effect refer to. We did
not want to call it a "race effect" as we were worried that may be interpreted
to mean the race of the athlete.  We did not think it would be informative to 
add and effect for individual runner's average ability as the majority of
observations in the data come from runners with very few (1-3) data points,
so taking an average of such a small sample may not be informative, especially
if there are outliers or an athlete had a bad start.

@@

\end{comment}  
The second reviewer shared a similar sentiment about not effectively
presenting ideas so we we made improvements to the introduction section to try
and more clearly present our ideas.  We shortened the literature review to only
cite papers that were actually of interest to the paper and tried to clearly
define the two purposes of the paper: to decide of 0.1 seconds is fair, and to
identify inconsistensies with the 2022 reaction times. We try to be precise in
our language as we do not have enough evidence to conclude that the sensors were
calibrated differently, or that Seiko (who make the timing devices) is at fault
for the 2022 reaction times being inexplicably faster. Thus we make general
recommendations for World Athletics and note that the reaction times in 2022
were unusually fast with no clear reason.

@@

We have re-worked the introduction and discussion sections of the paper to more
clearly outline the goals of the paper.  The organization of the paper was
something that both reviewers commented on so we did our best to try and
streamline the two key points of the paper: to decide of 0.1 seconds is fair,
and to identify inconsistensies with the 2022 reaction times. With these two
points emphasized we tried to remove sections that did not support these central
ideas.  In regards to the language surrounding the rank comparison text and the
timing device at the 2022 Championships we are intentionally vague as we do not
have evidence to make a stronger claim.  For example, we cannot claim that the
timing device was faulty as miscalibrated as there is no public information
available about that.  We do not want to overstep and put ourselves or the
publication at risk of defamation claims from Seiko because we called their
devices faulty when they are not.  Instead we suggest to the reader that 2022
was an unusually fast year and comment that there is no explanation as to why
athletes improve reaction times over the span of a few months and let the reader
decide what they think is the underlying cause of the faster reaction times.

@@

Unfortunately data such as this is not easy to come by.  We found as much as we
could online, but there is simply not enough data to justify a formal analysis
of his reaction times across lower level meets.  Many track and field races do
not record data on reaction times until at the very high level (national
and world championship).  Simply put, reaction times are not heavily researched
and thus the data material in insufficient.
